---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```



# stargate

<!-- badges: start -->
<!-- badges: end -->

The goal of **stargate** package is to simplify production of formatted tables that hold regression analysis results from several models side-by-side.

For many years, we have used **stargazer** package for this purpose. **stargazer** is great and every applied econometrician has to be thankful to Marek Hlaváč for kindly providing it. However, this package is implemented as one monolithic function, which has two drawbacks: 

1. It is very difficult for an user to implement a method for an estimated object not covered in **stargazer**.
2. It has too many complex parameters. A set of lightweight manipulation function joined with pipes (in the tidyverse style) seems preferable.
3. It has its own output filters to LaTeX, HTML, etc., and hence it is impossible to customize output for your own liking.

This package is an attempt to rewrite **stargazer** remove these obstacles. To pay homage to the original package, it is named similarly: **stargate**.

1. Every estimated object class should have its own method to convert the estimate into a standard format. The broom is used now but dedicated methods would be provided later to customize the process, e.g.\ to include robust SEs.
2. The workflow must be based on simples function that send their outputs between themselves through pipes.
3. The final output must be a *tibble* (convertible to *data.frame*, etc.), and hence everyone can create the final table with any tool that suits him or her, e.g.\ `kbl()` from **kableExtra**.

However, this package is just in a rudimentary state---it is more a proof of the concept and a playground than a real thing. It is here to raise some feedback, comments, and wishes. If used, it must be used with extreme care:

* It can handle only the estimates handled by **broom** at the present time.
* Anything can change at any time.
* Anything can fail you expectations at any time.

You have been warned. Enjoy!



## Installation

<!--
You can install the released version of stargate from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("stargate")
```
-->

At the present time, there is only the development version. It is available from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("mkvasnicka/stargate")
```



## Example

This is a basic example which shows you how to use **stargate**. Load the necessary packages first:

```{r packages}
library(stargate)
library(tibble)
library(kableExtra)
```

Estimates some models (simulated here):

```{r estimates}
n <- 1e3
df <- tibble(
    x1 = rnorm(n),
    x2 = rnorm(n),
    x3 = rnorm(n),
    e  = rnorm(n),
    y  = x1 - 2 * x2 + 3 * x3 + e
)

m1 <- lm(y ~ x1 + x2, df)
m2 <- lm(y ~ x1 + x2 + x3, df)
m3 <- lm(y ~ x1 + x2 * x3, df)
```

Convert the estimates to their **stargate** representation: one model with `sg_model()`, many models with `sg_table()`:

```{r sg models}
sm1 <- sg_model(m1)
stab <- sg_table(sm1, m2, m3)
```

Transform the model table to your liking:

```{r sg transform}
stab <- stab |>
    sg_remove(coefs = "Interc", regex = TRUE) |> 
    sg_remove(stats = c("r.squared", "logLik", "nobs"), keep = TRUE)
```

Format the table:

```{r sg format}
sftab <- stab |> 
    sg_format()
```

Present:

```{r}
sftab <- sftab |> 
    sg_present()
```


Print the table:

```{r}
kbl(sftab, format = "pipe") |> 
    kable_classic()
```

Or do all that at once:

```{r sg all}
sg_table(sm1, m2, m3) |> 
    sg_remove(coefs = "Interc", regex = TRUE) |> 
    sg_remove(stats = c("r.squared", "logLik", "nobs"), keep = TRUE) |> 
    sg_format(nsmall = 3) |> 
    sg_present() |> 
    kbl(format = "pipe") |> 
    kable_classic()
```



## What next

* Implement the stuff. :-)
* Provide methods for estimation objects.
* Write a vignette how to write a new method.
* Provide some auto-setup for the function to simplify the process.
* Tune the output to LaTeX, HTML, Markdown, and possibly Word/LibreOffice.
