---
title: "How to create a new model method"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{How to create a new model method}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
# library(stargate)
```

This vignette discusses why and how create a new `sg_model()` method. 



## Why new methods for `sg_model()`

Let's see it in the case of **fixest** package. The package allows us to do several things at once: to estimate fixed effects, to compute heteroskedastic clustered standard errors, etc. Let's see a simple example modified from its vignette. It estimate a Poisson model with four fixed effects, heteroskedastic standard errors clustered on Origin:

```{r}
library(fixest)
data(trade)
gravity_pois <- fepois(Euros ~ log(dist_km) | Origin + Destination + Product + Year,
                       se = "hetero",
                       trade)
```

**fixest** origina function presents all these pieces of information in a nice table:

```{r}
etable(gravity_pois)
```

However, these pieces are partially lost with the `summary()` function:

```{r}
summary(gravity_pois)
```

They are *completely* lost with **broom**'s `tidy()` function:

```{r}
library(broom)
tidy(gravity_pois)
```

As the default method of `sg_model()` uses **broom**'s `tidy()` and `glance()` functions, the information is lost too. This way, we have only three options: 

1. We stick with **fixest**'s `etable()`. This way we have to use a special presentation function for each estimation package we use---and we cannot mix estimates from different packages in one table. Moreover, most packages simply do not provide such a nice function as **fixest** does.

2. We use the default method of `sg_model()`. This way we can use the same workflow for every estimation package we use (provided that **broom** has methods for it) and we can combine different models in one table. However, we loose important pieces of information.

3. We write a new method for `sg_model()` which keeps all the information.

Moreover, there are two other reasons to write new `sg_model()` methods:

1. **broom** does not implement `tidy()` and `glance` for each estimation function in the wild and these packages provide at most a specific method of `summary()` function. In this case, the new method of `sg_model()` may be our only chance.
2. Even when there is a **broom** method, it does not cover well various ways to compute standard errors.


## The structure of *sg_model* class

A *sg_model* class is a list with the class attribute set to `c("sg_model", "stargate")`. Presently, it has three slots---each of them is a *tibble*

* `coefs` ... the estimated coefficients; in the default method, the result of `broom::tidy()`
* `stats` ... the model statistics---one statistic per row, each enveloped in a list (i.e.\ the value column is a list); in the default mehtods, the result of `broom::glance()` enveloped in list and pivotted longer
* `name` ... the model's name (`""` if not set)

The look at the default method shows more precisely how it looks like:

```{r, eval=FALSE}
sg_model.default <- function(m, name = "", ...) {
    if (inherits(m, "stargate"))
        return(m)
    coefs <- broom::tidy(m)
    stats <- broom::glance(m) |>
        dplyr::mutate(dplyr::across(dplyr::everything(), list)) |>
        tidyr::pivot_longer(dplyr::everything(),
                            names_to = "stat", values_to = "val")
    name <- tibble::tibble(name = name)
    structure(list(coefs = coefs, stats = stats, name = name),
              class = c("sg_model", "stargate"))
}
```

The present structure is not sufficient to cover the results of **fixest**'s estimation functions. It lacks at least two things:

1. the ability to include "word" parameters, e.g.\ "Yes" for the fixed effects and
2. the ability to keep the information on the kind of standard errors the model estimates, e.g.\ "heteroskedasticity-robust"

There are many ways how to handle it:

1. "word parameters":
    - add them to `coefs` table to the `estimate` column---it would have to be a list column
    - create a new table
    - ???
2. standard error information:
    - add them to `stats` table
    - add a new table
    - ???

It is necessary to design how to include these things into the data structure. Moreover, it is necessary to find out which other items are presently missing to make the structure rich enough to be able to encompass most of the estimated models without a loss of information.

*TODO*



## How to write a new `sg_model()` method

*TODO*
